Combinatorial interpretations of holonomic recurrences

### 2021-09-04 article/main.tex
Add unary-binary proof
Fixups

@@

Next, in the section \ref{sec:known_results}, we present known results. They demonstrate combinatorial interpretations that resemble different approaches.

@@

\begin{center}
    \begin{longtable}{| c | c | c |}
        \hline

        \(U(n-2)\) &
        \(U(n-1)\) &
        \(U(n)\)\\
        \hline

        &
        I \includesvg[scale=0.4]{unary_binary__1si} &
        Vro \includesvg[scale=0.4]{unary_binary__0fid} \\
        \hline

        &
        Vlt \includesvg[scale=0.4]{unary_binary__1fjg} &
        VrtUrv \includesvg[scale=0.4]{unary_binary__0fjdOgf} \\
        \hline

        I \includesvg[scale=0.4]{unary_binary__2i} &
        &
        VrtUra \includesvg[scale=0.4]{unary_binary__0fjdOdi} \\
        \hline

        &
        Vro \includesvg[scale=0.4]{unary_binary__1fid} &
        VrtUla \includesvg[scale=0.4]{unary_binary__0fjdOgi} \\
        \hline

        &
        Vrt \includesvg[scale=0.4]{unary_binary__1fjd} &
        VltUrv \includesvg[scale=0.4]{unary_binary__0fjgOdf} \\
        \hline

        I \includesvg[scale=0.4]{unary_binary__2i} &
        &
        VltUra \includesvg[scale=0.4]{unary_binary__0fjgOdi} \\
        \hline

        I \includesvg[scale=0.4]{unary_binary__2i} &
        &
        VltUla \includesvg[scale=0.4]{unary_binary__0fjgOgi} \\
        \hline
    \end{longtable}
\end{center}

@@

It is easy to show that it constructs bijection between \((n + 1) T(n + 1)\) and subset of \(\{L_1, L_2, R_1\} \times (2 n - 1) T(n)\) not falling into case 3.

@@

>>>>

\newcommand{\mhlr}[1]{{\tikzmarkin[set fill color=red!30,set border color=red]{highlight-\arabic{highlightid}}(0.02,-0.15)(-0.02,0.35){#1}\tikzmarkend{highlight-\arabic{highlightid}}\stepcounter{highlightid}}}
\newcommand{\mhlg}[1]{{\tikzmarkin[set fill color=green!30,set border color=green]{highlight-\arabic{highlightid}}(0.02,-0.15)(-0.02,0.35){#1}\tikzmarkend{highlight-\arabic{highlightid}}\stepcounter{highlightid}}}
\newcommand{\mhlb}[1]{{\tikzmarkin[set fill color=blue!30,set border color=blue]{highlight-\arabic{highlightid}}(0.02,-0.15)(-0.02,0.35){#1}\tikzmarkend{highlight-\arabic{highlightid}}\stepcounter{highlightid}}}

@@

Next, in the section \ref{sec:known_results}, we present known results. They demonstrate combinatorial interpretations that reflect different approaches.

@@

\begin{center}
    \begin{longtable}{| c | c | c | c |}
        \hline

        \(U(n-2)\) &
        \(U(n-1)\) &
               &
        \(U(n)\)\\
        \hline

        &
        I \includesvg[scale=0.4]{unary_binary__1si} &
        \(\Rightarrow\)&
        Vro \includesvg[scale=0.4]{unary_binary__0fid} \\
        \hline

        &
        Vlt \includesvg[scale=0.4]{unary_binary__1fjg} &
        \(\Rightarrow\)&
        VrtUrv \includesvg[scale=0.4]{unary_binary__0fjdOgf} \\
        \hline

        I \includesvg[scale=0.4]{unary_binary__2i} &
        &
        \(\Rightarrow\)&
        VrtUra \includesvg[scale=0.4]{unary_binary__0fjdOdi} \\
        \hline

        &
        Vro \includesvg[scale=0.4]{unary_binary__1fid} &
        \(\Rightarrow\)&
        VrtUla \includesvg[scale=0.4]{unary_binary__0fjdOgi} \\
        \hline

        &
        Vrt \includesvg[scale=0.4]{unary_binary__1fjd} &
        \(\Rightarrow\)&
        VltUrv \includesvg[scale=0.4]{unary_binary__0fjgOdf} \\
        \hline

        I \includesvg[scale=0.4]{unary_binary__2i} &
        &
        \(\Rightarrow\)&
        VltUra \includesvg[scale=0.4]{unary_binary__0fjgOdi} \\
        \hline

        I \includesvg[scale=0.4]{unary_binary__2i} &
        &
        \(\Rightarrow\)&
        VltUla \includesvg[scale=0.4]{unary_binary__0fjgOgi} \\
        \hline
    \end{longtable}
\end{center}

@@

It is easy to show that it constructs bijection between \((n + 1) T(n + 1)\) and subset of \(\{L_1, L_2, R_1\} \times (2 n - 1) T(n)\) not falling into case 3. We will show that in a moment.

@@

To see the bijection, we can just draw all possible cases:

\begin{center}
    \begin{longtable}{| c | c | c | c | c |}
        \hline
        &
        \(\Rightarrow\)&
        \(R_1\) &
        \(L_1\) &
        \(L_2\) \\
        \hline

        \includeinlinescaledsvg{.23}{.35}{schroder__proof__21} &
        \(\Rightarrow\)&
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__23} &
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__22} &
        \begin{minipage}{.23\textwidth}
            \begin{center}
                \includeinlinescaledsvg{1}{.35}{schroder__proof__24}
                \(\Downarrow\)
                \includeinlinescaledsvg{1}{.35}{schroder__proof__24b}
            \end{center}
        \end{minipage}
        \\
        \hline

        \includeinlinescaledsvg{.23}{.35}{schroder__proof__11} &
        \(\Rightarrow\)&
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__13} &
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__12} &
        \begin{minipage}{.23\textwidth}
            \begin{center}
                \includeinlinescaledsvg{1}{.35}{schroder__proof__14}
                \(\Downarrow\)
                \includeinlinescaledsvg{1}{.35}{schroder__proof__14b}
            \end{center}
        \end{minipage}
        \\
        \hline

        \includeinlinescaledsvg{.23}{.35}{schroder__proof__31} &
        \(\Rightarrow\)&
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__33} &
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__32} &
        \begin{minipage}{.23\textwidth}
            \begin{center}
                \includeinlinescaledsvg{1}{.35}{schroder__proof__34}
                \(\Downarrow\)
                \includeinlinescaledsvg{1}{.35}{schroder__proof__34b}
            \end{center}
        \end{minipage}
        \\
        \hline

        \includeinlinescaledsvg{.23}{.35}{schroder__proof__51} &
        \(\Rightarrow\)&
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__53} &
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__52} &
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__54} \\
        \hline

        \includeinlinescaledsvg{.23}{.35}{schroder__proof__41} &
        \(\Rightarrow\)&
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__43} &
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__42} &
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__44} \\
        \hline

        \includeinlinescaledsvg{.23}{.35}{schroder__proof__61} &
        \(\Rightarrow\)&
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__63} &
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__62} &
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__64} \\
        \hline

        \includeinlinescaledsvg{.23}{.35}{schroder__proof__71} &
        \(\Rightarrow\)&
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__73} &
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__72} &
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__74} \\
        \hline

        \includeinlinescaledsvg{.23}{.35}{schroder__proof__81} &
        \(\Rightarrow\)&
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__83} &
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__82} &
        \includeinlinescaledsvg{.23}{.35}{schroder__proof__84} \\
        \hline

    \end{longtable}
\end{center}

In the left column you can see all possibilities of selecting \(s\) from a tree of size \(n\). In \(R_1\), \(L_1\) and \(L_2\) columns we show how they are then transformed. It covers all possible cases of selecting leaf from a tree of size \(n + 1\) and selecting an internal from a tree of size \(n - 1\).
